\documentclass[notes,mh]{mikoslides}
\libinput{preamble}
\begin{document}
\begin{module}[id=mathtalk-definitions]
  \importmhmodule[dir=dmath/en]{mathtalk}
  \gimport[smglom/sets]{fundefeq}

\begin{note}
\begin{omtext}
  Mathematics uses a very effective technique for dealing with conceptual complexity. It
  usually starts out with discussing simple, {\emph{basic}} objects and their
  properties. These simple objects can be combined to more complex, {\emph{compound}}
  ones. Then it uses a definition to give a compound object a new name, so that it can be
  used like a basic one. In particular, the newly defined object can be used to form
  compound objects, leading to more and more complex objects that can be described
  succinctly. In this way mathematics incrementally extends its vocabulary by add layers
  and layers of definitions onto very simple and basic beginnings. We will now discuss
  four definition schemata that will occur over and over in this course.
\end{omtext}

\begin{definition}[id=simpledef.def,for={eqdef,defeq}]
  The simplest form of definition schema is the \defii{simple}{definition}. This just
  introduces a name (the \defi{definiendum}) for a compound object (the
  \defi{definiens}). Note that the name must be new, i.e. may not have been used for
  anything else, in particular, the definiendum may not occur in the definiens. We use the
  symbols $\defeqOp$ (and the inverse $\eqdefFN$) to denote simple definitions in formulae.
 \end{definition}

 \begin{example}[id=one.def,for=simpledef.def]
   \usemhmodule[dir=dmath/en]{nat-basic}
   We can give the unary natural number $\sslash{\sslash{\sslash{\sslash\szero}}}$ the
   name $\phi$. In a formula we write this as
   $\defeq\phi{\sslash{\sslash{\sslash{\sslash\szero}}}}$ or
   $\eqdef{\sslash{\sslash{\sslash{\sslash\szero}}}}\phi$.
 \end{example}

\begin{definition}[id=pattern.def,for=defequiv]
  A somewhat more refined form of definition is used for operators on and relations
  between objects. In this form, then definiendum is the operator or relation is applied
  to $n$ distinct variables $\naseqli{v}1n$ as arguments, and the definiens is an expression
  in these variables. When the new operator is applied to arguments $\naseqli{a}1n$, then
  its value is the definiens expression where the $\livar{v}i$ are replaced by the
  $\livar{a}i$. We use the symbol $\defeqOp$ for operator definitions and $\defequivOp$
  for pattern definitions.\ednote{maybe better markup up pattern definitions as binding
    expressions, where the formal variables are bound.}
\end{definition}

\begin{example}[id=patterndef.fex,for=pattern.def]
  \guse[smglom/sets]{intersection}
  \guse[smglom/sets]{emptyset}
  The following is a pattern definition for the set intersection operator $\intersectOp$:
  \[\fundefeq{A,B}{\intersect{A,B}}{\bsetst{x}{x}{\conj{\inset{x}{A},\inset{x}{B}}}}\]
  The pattern variables are $A$ and $B$, and with this definition we have e.g.
  $\intersect{\eset,\eset}=\setst{x}{\conj{\inset{x}\eset,\inset{x}\eset}}$.
\end{example}

\begin{definition}[id=implicitdef.def]
  We now come to a very powerful definition schema. An \defii{implicit}{definition}
  (also called \defii[name=definition-by-description]{definition}{by description}) is a
  formula $\bA$, such that we can prove $\uexis{n}\bA$, where $n$ is a new name.
\end{definition}

\begin{example}[id=implicitdef.ex,for=implicitdef.def]
  \guse[smglom/sets]{set}
  \guse[smglom/sets]{emptyset}
  $\foral{x}{\inset{x}\eset}$ is an implicit definition for the empty set $\eset$. Indeed
  we can prove unique existence of $\eset$ by just exhibiting $\eset[braces]$ and showing
  that any other set $S$ with $\foral{x}{\ninset{x}S}$ we have
  $\setequal{S,\eset}$. Indeed$S$ cannot have elements, so it has the same elements ad
  $\eset$, and thus $\setequal{S,\eset}$.
\end{example}
\end{note}
\end{module}


\end{document}
% LocalWords:  en mathtalk disjFN disj conjFN conj implyFN biimplFN biimpl sdot
% LocalWords:  foralFN foral exisFN exis uexis negateFN MathTalk stex dmath eqd
% LocalWords:  eqdFN defequivOp defequiv defeq natsymdef
% LocalWords:  mathrel nobrackets Leftrightarrow omgroup omtext emph defii defi
% LocalWords:  simpledef.def sslash sslash sslash sslash szero seqli ednote
% LocalWords:  patterndef.thy patterndef.ex setst eset eset eset eset ninset
% LocalWords:  implicitdef.def implicitdef.thy implicitdef.ex setequal usevocab
